---
title: "Glovo_Project"
author: "Victor Vu"
date: "23/03/2019"
output: html_document
---

#Download The Required Packages

```{r}
library("Matrix")
library("recommenderlab")
library("dplyr")
library(data.table)
```

# Load review dataset which includes business, user and review data

```{r}
# Data was subsetted to only include restaurant categories 
review <- read.csv("review.csv")
# Remove Duplicated Rows 
set.seed(123)
rating <<- review %>% distinct(user_id, business_id, .keep_all = TRUE)
```

#Creating Unique Row and Column out of User_ID and Business_ID 

```{r}
row <- data.frame(user_No= seq(1:length(unique(rating[,"user_id"]))),user_id= unique(rating[,"user_id"]))
column <- data.frame(restaurant_No= seq(1:length(unique(rating[,"business_id"]))),business_id=unique(rating[,"business_id"]))

#Merge the column and row with initial rating dataset
rating <- merge(rating,row,by.x='user_id',by.y='user_id')
rating <- merge(rating,column,by.x='business_id',by.y='business_id')
```

# Build the rating matrix out of unique rows and columns 

```{r}
matrix <- data.frame(
  user =   rating$user_No, 
  restaurant =  rating$restaurant_No, 
  stars = rating$stars
)
set.seed(123)
rating_matrix <- as(matrix,"realRatingMatrix")
getRatingMatrix(rating_matrix)[1:10,1]
```

# Check if there are abnormal ratings in the dataset

FALSE indicates that there are no abnormal values
```{r}
table(rating_matrix@data@x[] > 5) 
table(rating_matrix@data@x[] < 1) 
```

# Build a Switching Hybrid Model. Apply Popularity to new and inactive user and use Hybrid weighted model for active user with more than 5 ratings.

```{r cars}
trainAlgorithm <- function(data) {
  weighted_hybrid <<- HybridRecommender(
      Recommender(data, method="POPULAR"),
      Recommender(data, method = "IBCF", 
                  param=list(normalize = "Z-Score", method="Cosine", k=50)),
      Recommender(data, method="RANDOM"),
      weights = c(0.09,0.9,0.01))
  popularity <<- Recommender(data, method="POPULAR")
}

applyAlgorithm <- function(data) {
  if (rowCounts(data) > 5) {
    print("Hybrid Reccomender applied to Active User")
    pred <<- predict(weighted_hybrid, data, type="topNList", n = 10)
  } else {
      print("Popularity Reccomender applied to Non-active User")
      pred <<- predict(popularity, data, type="topNList", n = 10)   
  }
  return(as(pred, "list"))
}
```

# Applied Location Based Recommender To Filter Result To Only Las Vegas
```{r}
set.seed(123)
target_restaurants <- unique(rating[rating$city == 'Las Vegas','restaurant_No'])
filtered_restaurants <- rating_matrix[,target_restaurants]
# For training purpose, only keep users and restaurants with higher than 10 ratings
filtered_restaurants <- filtered_restaurants[rowCounts(filtered_restaurants) > 10, colCounts(filtered_restaurants) > 10]
```

# Recommend To User 10 based in Las Vegas

Explore the ratings of User 10 

```{r}
userRatings <- as(filtered_restaurants[50,], "list")[[1]]
restaurantsWithRatings <- data.frame(names(userRatings))
colnames(restaurantsWithRatings) <- "restaurant_No"

#Merge The Ratings Of User 10 with the Review Dataset to extract information about each rating
restaurantsWithRatings <- (merge(restaurantsWithRatings,rating,by='restaurant_No'))[,c(4,11,5,9)]
restaurantsWithRatings <- restaurantsWithRatings %>% distinct(business_name, .keep_all = TRUE)
restaurantsWithRatings 
```

#Train the model and obtain recommendations 
```{r}
trainAlgorithm(filtered_restaurants)
```

# Apply The Model to User 10 

```{r}
applyAlgorithm(filtered_restaurants[50,])
```

# Explore the recommendations for User 10 

```{r}
pred_restaurant <-  data.frame(as(pred, "list"))
colnames(pred_restaurant) <- "restaurant_No"

# Join the prediction dataframe with a dataframe that contain customer name 
pred_restaurant <- (merge(pred_restaurant,rating, by='restaurant_No'))[,c(4,5,9)]
pred_restaurant <- pred_restaurant %>% distinct(business_name, .keep_all = TRUE)
pred_restaurant
```

# Apply Knowledge Based Recommender To Only Recommend only Mexican Restaurant 

```{r}
pred_restaurant[pred_restaurant$business_categories %like% "Mexican",]
```

# Applied Context Specific Recommendation To Recommend on restaurants in Las Vegas that serve   Breakfast

```{r}
set.seed(123)
breakfast_restaurants <- unique(rating[rating$city == 'Las Vegas' & rating$business_categories %like% "Breakfast",'restaurant_No'])
filtered_breakfast <- rating_matrix[,breakfast_restaurants]
# For training purpose, only keep users and restaurants with higher than 10 ratings
filtered_breakfast <- filtered_breakfast[rowCounts(filtered_breakfast) > 0, colCounts(filtered_breakfast) > 0]
```

# Test Context Specific Recommendation on User 1. This is a new User that based in Vegas and would like to have Juice & Smoothies for Breakfast


```{r}
userRatings <- as(filtered_breakfast[1,], "list")[[1]]
restaurantsWithRatings <- data.frame(names(userRatings))
colnames(restaurantsWithRatings) <- "restaurant_No"

#Merge The Ratings Of User 10 with the Review Dataset to extract information about each rating
restaurantsWithRatings <- (merge(restaurantsWithRatings,rating,by='restaurant_No'))[,c(4,11,5,9)]
restaurantsWithRatings <- restaurantsWithRatings %>% distinct(business_name, .keep_all = TRUE)
restaurantsWithRatings 
```

#Train the model and obtain recommendations

```{r}
trainAlgorithm(filtered_breakfast)
applyAlgorithm(filtered_breakfast[1,])
```

# Explore the recommendations for User 1. 
```{r}
pred_restaurant <-  data.frame(as(pred, "list"))
colnames(pred_restaurant) <- "restaurant_No"

# Join the prediction dataframe with a dataframe that contain customer name 
pred_restaurant <- (merge(pred_restaurant,rating, by='restaurant_No'))[,c(4,5,9)]
pred_restaurant <- pred_restaurant %>% distinct(business_name, .keep_all = TRUE)
pred_restaurant
```

# Knowledged Based Recommender is applied to restaurants that has Juice & Smoothies

```{r}
pred_restaurant[pred_restaurant$business_categories %like% "Juice Bars",]
```



